Optimization of wide-band quasi-omnidirectional 1-D photonic structures

### 2021-04-28 PaperVictor.tex
Describe the changes to table 3 in the text and highlight changes

% !TeX spellcheck = en_US
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[numbers]{natbib}
%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%
\usepackage{braket}
\usepackage{bm}

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
\shortauthors{V. Castillo-Gallardo et~al.}

@@

Finally, Table \ref{tab:table3} shows data from some porous
silicon based ODM designed to operate in the NIR
region and their of the ODB's are compared with those of
the structures analyzed in the present study. The ODW
of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
the ODB of the structure $S_3$ begins at 950 nm like the one
synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
nm. In other words, $S_3$ has an ODW 3.55 times higher. Moreover, the
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
\% of the ODW of our $S_2$ and $S_3$ structures. Aditionally, the table
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
As compared to the previous studies \cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
opens the possibility of generating dielectric multilayered
structure with large omnidirectional band with
the materials with relatively low refractive index contrast.

\begin{table}
        \centering
        \begin{tabular}{rrrrrr}
                Reference&Year&Sample&ODB (nm)&AR ($^\circ$)&ODW (nm)\\
                \hline
                \hline
                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&0-80&340\\
                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&0-89&318\\
                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&8-68&506\\
                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&8-65&1000\\
                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&0-80&1321\\
                \hline
                &    &$S_1$&980-1340&10-60&360 \\
                This work                               &2021&$S_2$&980-2780&10-60&1800\\
                &    &$S_3$&950-2750&10-60&1800\\
        \end{tabular}
        \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
                previously published works (first block) and for the different samples studied here (second
                block). We show the attained omnidirectional bands (ODB) in the angular range (AR) and their widths (ODW).}
        \label{tab:table3}
\end{table}

>>>>

% !TeX spellcheck = en_US
\documentclass[a4paper,fleqn]{cas-sc}
\usepackage[numbers]{natbib}
%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}
%%%
\usepackage{braket}
\usepackage{bm}
\usepackage{xcolor}
\newcommand{\hl}[1]{{\color{blue}#1}}
\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Optimization of wide-band quasi-omnidirectional 1-D photonic structures}
\shortauthors{V. Castillo-Gallardo et~al.}

@@

Finally, Table \ref{tab:table3} shows data from some porous
silicon based ODM \hl{and quasi-ODM designed to operate in the NIR
region and their (quasi) ODB's are compared with those of
the structures analyzed in the present study. The quasi-ODW}
of the structure $S_1$ results 20 nm wider than that reported by Bruyant,
et al. \cite{Bruyant2003} and it is located closer to the visible range. Furthermore,
\hl{the quasi-ODB of the structure $S_3$} begins at 950 nm like the one
synthesized by Estevez, et al. \cite{Estevez2009}; nevertheless, its width extends to 2750
nm. In other words, $S_3$ has \hl{a quasi-ODW 3.55 times larger}. Moreover, the
ODW of the structure reported by Xifre-Perez, et al. \cite{Xifre2005} represents only 17.6
\% of the \hl{quasi-ODW of our $S_2$ and $S_3$ structures}. Aditionally, the table
reveals that the porous silicon based
structures $S_2$ and $S_3$ have the widest gap widths, 1.36 times greater than the
largest reported work until now in the NIR region \cite{Wu2021}.
As compared to the previous studies
\cite{Bruyant2003,Estevez2009,Xifre2005,Wu2021,Fink1998}, this work
opens the possibility of generating dielectric multilayered
\hl{structures with large quasi-omnidirectional bands with pairs of
materials that have a relatively low refractive index contrast. To be
fair, we have to point out that the (quasi) omnidirectional band widths of the
structures compared above correspond to different angular ranges,
which are defined by instrumental constrictions.}

\begin{table}
        \centering
        \begin{tabular}{rrrrrr}
                Reference&Year&Sample&\emph{q}-ODB (nm)&\hl{AR (degrees)}&\emph{q}-ODW (nm)\\
                \hline
                \hline
                Bruyant, et al. \cite{Bruyant2003}      &2003&-    &1100-1440&\hl{0-80}&340\\
                Xifre-P\'{e}rez, et al. \cite{Xifre2005}&2004&-&1297-1615&\hl{0-89}&318\\
                Estevez, et al. \cite{Estevez2009}      &2009&-    &950-1456&\hl{8-68}&506\\
                Chavez, et al. \cite{Chavez2020}        &2020&-    &1000-2000&\hl{8-65}&1000\\
                Wu, et al. \cite{Wu2021}                &2021&-    &1284-2605&\hl{0-80}&1321\\
                \hline
                &    &$S_1$&980-1340&\hl{10-60}&360 \\
                This work&2021&$S_2$&980-2780&\hl{10-60}&1800\\
                &    &$S_3$&950-2750&\hl{10-60}&1800\\
        \end{tabular}
        \caption{Development of porous silicon based omnidirectional mirrors for the NIR region for
                previously published works (first block) and for the different samples studied here (second
                block). We show the attained (quasi) omnidirectional
                bands (\emph{q}-ODB), the measured angular range (AR) and their widths (\emph{q}-ODW).}
        \label{tab:table3}
\end{table}
